### 2020-09-18 manuscript/ERL_global_C_review.Rmd
remove context on importance of forests beyond global C cycle/climate

*Background.* *The fate of Earth’s climate is closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate through their influential role in the global carbon (C) cycle. Synthetic understanding of global forest C cycles is needed to constrain model estimates of forest feedbacks to climate change and to more accurately quantify the influence of land use decisions on climate.*

@@

On an ecosystem level, forest C cycling is central to the flow of energy and materials, and as the basis of food webs...
(support of biodiversity)
(human reliance as source of food, fuel, fiber)

>>>>

*Background.* The fate of Earth’s climate is closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate through their influential role in the global carbon (C) cycle. Synthetic understanding of global forest C cycles is needed to constrain model estimates of forest feedbacks to climate change and to more accurately quantify the influence of land use decisions on climate.

@@
